Comparing Machine Learning algorithms for classifying cognitive states from fMRI data

### 2012-11-09 article/article.tex

%% indicate IEEE Member or Student Member in form indicated below
\author{Mattijs Meiboom, Robin Mills
, Tijn Schouten, Spyros Ioakeimidis}
\authorfooter{
\item
  Mattijs Meiboom is with University of Groningen, E-mail: m.meiboom@student.rug.nl.
\item
  Robin Mills is with University of Groningen, E-mail: r.mills@student.rug.nl.
\item
  Tijn Schouten is with University of Groningen, E-mail: t.m.schouten.2@student.rug.nl.
\item
  Spyros Ioakeimidis  is with University of Groningen, E-mail: s.ioakeimidis@studenr.rug.nl.
}

@@

- same for each algorithm:
    - What features did we select?
    - How did we train?
    - How did we test?
        - How did we calculate performance?
- algorithms:
    - gaussian naive-bayes (gnb)
        - pca + gnb
    - multivariate
    - svm

>>>>

%% indicate IEEE Member or Student Member in form indicated below
\author{Mattijs Meiboom, Robin Mills, Tijn Schouten, Spyros Ioakeimidis}
\authorfooter{
\item
  Mattijs Meiboom is with University of Groningen, E-mail: m.meiboom@student.rug.nl.
\item
  Robin Mills is with University of Groningen, E-mail: r.mills@student.rug.nl.
\item
  Tijn Schouten is with University of Groningen, E-mail: t.m.schouten.2@student.rug.nl.
\item
  Spyros Ioakeimidis  is with University of Groningen, E-mail: s.ioakeimidis@studenr.rug.nl.
}

@@

- same for each algorithm:
    - What features did we select?
    - How did we train?
    - How did we test?
        - How did we calculate performance?
- algorithms:
    - gaussian naive-bayes (gnb)
        - pca + gnb
    - multivariate
    - svm
    - why multivariate is not a priori better than naive: less assumption, higher generalizability, better estimation parameters.
